The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
List prior hypotheses

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r c l}
    \hline
    Symbol                & Expectation & Figure \\
    \hline
    \hline
    $\mathcal{H}_1$       & For a higher $s$, $e$ will increase monotonously & 1 \\
    $\mathcal{H}_2$       & Extinction rates have no effect on $e$ & 2 \\
    $\mathcal{H}_3$       & The timing of multiple-birth events has no effect on $e$ & 3 \\
    $\mathcal{H}_4$       & An MBD tree will have a higher $e$ than its twin BD counterpart & 4 \\
    $\mathcal{H}_5$       & The number of taxa has no effect on $e$ & 5 \\
    $\mathcal{H}_6$       & A higher number of taxa decreases the variance in $e$ & 6 \\
    $\mathcal{H}_7$       & The MBD regime has no effect on $e$ & 7 \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:hypotheses}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
